Denoising and Covariance Estimation of Cryo-EM Images

### 2017-02-10 echo_talk.tex
Removed timings slide from echo talk

@@

@@

\begin{frame}<beamer>
\frametitle{Computational Complexity}
$O(TDL^4 + nL^3)$, where $T$ is the number of conjugate gradient iterations
\begin{itemize}
\item $D$ defocus groups with $d_i$ images in group $i$
\item Images of size $L \times L$
\item \textit{n} images
\end{itemize}
\end{frame}

\begin{frame}<beamer>
\frametitle{Computational Complexity: Timings}
$n$ images of size $L \times L$\\
UNIX environment with 60 cores,
running at 2.3 GHz, with total RAM of 1.5TB

\begin{table}[t]
  \centering
  \caption{Timing in seconds}
  \begin{tabular}{ccccc}
    \toprule
    Dataset & $L$ & $n$ & Basis coeffs  & CWF \\
    \midrule
    TRPV1 & 256 & 35645 & 312s & 574s \\
    80s & 360 & 30000 &  731s & 385s \\
    IP3R1  & 256 & 37382 & 429s & 589s\\
    70s & 250 &  99979 & 1174s & 113s \\
 \bottomrule
  \end{tabular}
\end{table}
\end{frame}

>>>>

\begin{frame}
\frametitle{3D from 2D}
%  FEI
\begin{itemize}
 \item Insert pipeline flowchart
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Cryo-EM Pipeline}
%  FEI
\includegraphics[width=0.5\textwidth]{zika.png}%
\begin{itemize}
  \item Can't detect features from raw images, unlike SfM
 \item Need new algorithms to handle noise level!
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Open Source Software}
%  FEI
\includegraphics[width=0.5\textwidth]{zika.png}%
\begin{itemize}
  \item Insert ASPIRE image
  \item Open source software toolbox: ASPIRE
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Today's talk}
%  FEI
\includegraphics[width=0.5\textwidth]{zika.png}%
\begin{itemize}
  \item Pipeline figure: highlight denoising, class averaging
\end{itemize}
\end{frame}

@@

\begin{frame}<beamer>
\frametitle{Computational Complexity}
$O(TDL^4 + nL^3)$, where $T$ is the number of conjugate gradient iterations
\begin{itemize}
\item $D$ defocus groups with $d_i$ images in group $i$
\item Images of size $L \times L$
\item \textit{n} images
\end{itemize}
UNIX environment with 60 cores,
running at 2.3 GHz, with total RAM of 1.5TB
